My Title

### 2025-12-21 misc/collapse cheat sheet/collapse_cheat_sheet.Rnw
Update package website url to fastverse.org/collapse.

Calling \code{help("collapse-documentation")} brings up a detailed documentation, which is also available \href{https://fastverse.github.io/collapse/reference/index.html}{online}. See also the \href{https://fastverse.github.io/fastverse/}{\emph{fastverse}} package/project for a recommended set of complimentary packages and easy package management.
%}

@@

% \end{adjustbox}
%}
% \hrrule
\vspace{-5mm}
\textcolor{lightgray}{\hrulefill}\\
{\scriptsize \vspace{-0.5mm}
 Page 1 of 2 \hfill \href{https://creativecommons.org/licenses/by-sa/4.0/}{CC-BY-SA}\ Sebastian Krantz\ \textbullet\ Learn more at \href{https://fastverse.github.io/collapse/}{fastverse.github.io/collapse}\ \textbullet\ Source code at \href{https://github.com/fastverse/collapse}{github.com/fastverse/collapse}\ \textbullet\ Updates announced at \href{https://twitter.com/collapse\_R}{twitter.com/collapse\_R} - \#rcollapse\ \textbullet\ Cheatsheet created for \emph{collapse} version 2.0.3\ \textbullet\ Updated: 2023-10
}

@@

\vspace{-5.5mm}
\textcolor{lightgray}{\hrulefill}\\
{\scriptsize \vspace{-0.5mm}
 Page 2 of 2 \hfill \href{https://creativecommons.org/licenses/by-sa/4.0/}{CC-BY-SA}\ Sebastian Krantz\ \textbullet\ Learn more at \href{https://fastverse.github.io/collapse/}{fastverse.github.io/collapse}\ \textbullet\ Source code at \href{https://github.com/fastverse/collapse}{github.com/fastverse/collapse}\ \textbullet\ Updates announced at \href{https://twitter.com/collapse\_R}{twitter.com/collapse\_R} - \#rcollapse\ \textbullet\ Cheatsheet created for \emph{collapse} version 2.0.3\ \textbullet\ Updated: 2023-10
}

>>>>

Calling \code{help("collapse-documentation")} brings up a detailed documentation, which is also available \href{https://fastverse.org/collapse/reference/index.html}{online}. See also the \href{https://fastverse.org/fastverse/}{\emph{fastverse}} package/project for a recommended set of complimentary packages and easy package management.
%}

@@

% \end{adjustbox}
%}
% \hrrule
\vspace{-5mm}
\textcolor{lightgray}{\hrulefill}\\
{\scriptsize \vspace{-0.5mm}
 Page 1 of 2 \hfill \href{https://creativecommons.org/licenses/by-sa/4.0/}{CC-BY-SA}\ Sebastian Krantz\ \textbullet\ Learn more at \href{https://fastverse.org/collapse/}{fastverse.org/collapse}\ \textbullet\ Source code at \href{https://github.com/fastverse/collapse}{github.com/fastverse/collapse}\ \textbullet\ Updates announced at \href{https://twitter.com/collapse\_R}{twitter.com/collapse\_R} - \#rcollapse\ \textbullet\ Cheatsheet created for \emph{collapse} version 2.0.3\ \textbullet\ Updated: 2023-10
}

@@

\vspace{-5.5mm}
\textcolor{lightgray}{\hrulefill}\\
{\scriptsize \vspace{-0.5mm}
 Page 2 of 2 \hfill \href{https://creativecommons.org/licenses/by-sa/4.0/}{CC-BY-SA}\ Sebastian Krantz\ \textbullet\ Learn more at \href{https://fastverse.org/collapse/}{fastverse.org/collapse}\ \textbullet\ Source code at \href{https://github.com/fastverse/collapse}{github.com/fastverse/collapse}\ \textbullet\ Updates announced at \href{https://twitter.com/collapse\_R}{twitter.com/collapse\_R} - \#rcollapse\ \textbullet\ Cheatsheet created for \emph{collapse} version 2.0.3\ \textbullet\ Updated: 2023-10
}
